### 2022-05-29 article.tex
Must be 'article.bib'

A paper contains and/or describes data, where we define
data as 'individual facts, statistics, or items of information, often 
numeric' [OECD 2008].
To ensure unhampered knowledge growth, this data should [TODO: Why? Reference!] 
follow the FAIR 
principles.
The FAIR principles [Wilkinson et al., 2016] are that data should be 
[TODO: there are probably better examples]
Findable (e.g. found by web),
Accessible (e.g. DataDryad and or Zenoda), 
Interoperable (e.g. comma-separated files) 
and Reusable (e.g. work on all operating systems)

>>>>

A paper contains and/or describes data, where we define
data as 'individual facts, statistics, or items of information, often 
numeric' \cite{glossary2003oecd}.
To ensure unhampered knowledge growth, this data should [TODO: Why? Reference!] 
follow the FAIR 
principles.
The FAIR principles \cite{wilkinson2016fair} are that data should be 
[TODO: there are probably better examples]
Findable (e.g. found by web),
Accessible (e.g. DataDryad and or Zenoda), 
Interoperable (e.g. comma-separated files) 
and Reusable (e.g. work on all operating systems)
